Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features

### 2022-02-07 publication/manuscript.Rmd
prepare all files for LATEX upload of second revision to Computational Statistics

#date: "`r Sys.Date()`"
bibliography: literature.bib
#linenumbers: true
numbersections: true
output:
  #rticles::elsevier_article: default
  bookdown::pdf_book:
    base_format: rticles::springer_article
#bibstyle: spphys
csl: elsevier-harvard.csl

@@

```{r analysis-preferences, include=FALSE}
# Seed for random number generation (use old rng to be identical with master thesis)
RNGkind(sample.kind = "Rounding")
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo = FALSE)
options(knitr.kable.NA = " ")
# options(papaja.na_string = "")
```

>>>>

#date: "`r Sys.Date()`"
bibliography: literature.bib
#linenumbers: true
numbersections: true
output:
  #rticles::elsevier_article: default
  bookdown::pdf_book:
    base_format: rticles::springer_article
  keep_md: true
#bibstyle: spphys
csl: elsevier-harvard.csl

@@

```{r analysis-preferences, include=FALSE}
# Seed for random number generation (use old rng to be identical with master thesis)
RNGkind(sample.kind = "Rounding")
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo = FALSE, fig.path = "", dev=c('pdf', 'tiff'))
options(knitr.kable.NA = " ")
# options(papaja.na_string = "")
options(tinytex.clean = FALSE)
```
